---
title: "Lab 6"
author: "Erin de Leon Sanchez"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll make our own samples, using a pseudorandom generator

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test:
```{r}
t.test(gp_1, gp_2)
```

What is the meaning of the p-value? 
If these samples were drawn from populations with the same mean, the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%.

Retain (fail to reject) the null hypothesis. >> There is no significant difference in means between group 1 and group 2.

Warning: people get wirdly upset if you say "accept" the null.

Now let's compare this outcome to a rank-based test.

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

Meaning of p-value of 0.28:
If these samples were drawn from populations with the same ranks (medians), the probability of finding two samples with ranks *at least as different* as those in our samples is 0.28.

There is no significant difference in ranks (often you'll see medians) between group 1 and group 2 (statistical summary). 

Median scores for group 1 (M = 14) and group 2 (M = 12) did not differ significantly (Mann Whitney U test: U(df) = 86, p = 0.28)

To look at documentation:
type in `?wilcox.test` then you can recall values with `mwu$p.value`, etc.

## Linear regression

Simple linear regression (single dependent variable, a single independent variable)

```{r, include = FALSE}
# Make an exploratory plot of penguin body mass vs. flipper length (x-axis)

ggplot(data = penguins, aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_light()
```

Find a linear regression model using ordinary least squares describing the relationship between flipper length and body mass for these penguins. 

3 pieces:

- What type of model?
- What is the relationship to model (DV - IV(s))?
- Where is the data that's sued to create this model?

```{r}
penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)
```

y = mx + b
y is body mass
x is flipper length
body mass = 49.7(flipper length) - 5780.83
what is the coefficient for flipper length? The slope! On average, I expect for every one mm increase in flipper length, I expect a 49.7 gram increase in body mass! units = g/mm

-5780.08 units would be grams 
Interpretation: this intercept is not meaningful. Would have to extend flipper length to 0. 


### broom package returns model outputs as tidy data frames

```{r}
penguin_lm_tidy <- broom::tidy(penguin_lm)

broom::glance(penguin_lm) #gives model-wide uncertainties and whatnot in a nice data frame - more on Wednesday
```


How can I actually include my model equation in a report?

```{r}
extract_eq(model = penguin_lm, use_coefs = TRUE)
```

```{r}
plot(penguin_lm)
```

