---
title: "Lab 6"
author: "Erin de Leon Sanchez"
date: "11/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Example of a rank-based test

We'll make our own samples, using a pseudorandom generator

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

```{r}
hist(gp_1)

hist(gp_2)
```

Try a t-test:
```{r}
t.test(gp_1, gp_2)
```

What is the meaning of the p-value? 
If these samples were drawn from populations with the same mean, the probability of taking two random samples with means *at least as different* as the sample means we found by random chance (taking into account spread, n) is 19.8%.

Retain (fail to reject) the null hypothesis. >> There is no significant difference in means between group 1 and group 2.

Warning: people get wirdly upset if you say "accept" the null.

Now let's compare this outcome to a rank-based test.

## Mann Whitney U unpaired rank-based test

```{r}
mwu <- wilcox.test(gp_1, gp_2)

mwu
```

Meaning of p-value of 0.28:
If these samples were drawn from populations with the same ranks (medians), the probability of finding two samples with ranks *at least as different* as those in our samples is 0.28.

There is no significant difference in ranks (often you'll see medians) between group 1 and group 2 (statistical summary). 

Median scores for group 1 (M = 14) and group 2 (M = 12) did not differ significantly (Mann Whitney U test: U(df) = 86, p = 0.28)